Analyzing MLG distribution

### 2017-09-06 doc/RMD/MLG-distribution.Rmd
remove "arms" from labels in MLG-distributions

plot_mlg_graph <- function(g, glayout = NULL, label = TRUE, seed = 2017-06-28){
  set.seed(seed)
  if (is.null(glayout)){
    glayout <- layout_nicely(g)
    colnames(glayout) <- c("x", "y")
  } else {
    glayout <- glayout[V(g)$name, ]
  }
  shared_mlg  <- V(g)$weight * V(g)$size
  g           <- add_vertices(g, length(V(g)), size = V(g)$size - shared_mlg, color = "grey90")
  g2          <- g
  V(g2)$label <- ifelse(!is.na(V(g2)$name), sprintf("%s [(%d/%d)]", V(g2)$name, shared_mlg, V(g2)$size), NA)
  glay        <- create_layout(g2, "manual", node.positions = as.data.frame(rbind(glayout, glayout)))
  x_nudge     <- ifelse(abs(glay$x) == 1, -glay$x/10, glay$x/10)
  breaks      <- quantile(1 - E(g)$weight)
  breaks      <- setNames(breaks, format(breaks, digits = 2))
  outg <- ggraph(glay) +
    geom_edge_fan(aes(alpha = 1 - weight, width = width + 1)) +
    geom_node_circle(aes(r = drop(scale(size, center = FALSE))/10, fill = size))
  outg <- if (label) outg + geom_node_label(aes(label = label), repel = TRUE, parse = TRUE, label.size = 0.75, nudge_x = x_nudge) else outg
  outg + 
    viridis::scale_fill_viridis(option = "C") +
    scale_edge_alpha_continuous(range = c(1, 0.25), breaks = rev(breaks)) +
    scale_edge_width_continuous(range = c(0.25, 1.25), breaks = c(2:5)) +
    coord_fixed() +
    theme_void() +
    theme(text = element_text(size = 14)) +
    labs(list(
     # title = "Shared MLGs across regions",
      fill = "Number of\nMLHs",
      edge_alpha = "Probability of\nsecond encounter",
      edge_width = "Populations\nper MLH"#,
      #caption = "Outer circle: Number of MLGs in the region\nInner Circle: Number of private MLGs in the region"
    ))
}

>>>>

plot_mlg_graph <- function(g, glayout = NULL, label = TRUE, seed = 2017-06-28){
  set.seed(seed)
  if (is.null(glayout)){
    glayout <- layout_nicely(g)
    colnames(glayout) <- c("x", "y")
  } else {
    glayout <- glayout[V(g)$name, ]
  }
  shared_mlg  <- V(g)$weight * V(g)$size
  g           <- add_vertices(g, length(V(g)), size = V(g)$size - shared_mlg, color = "grey90")
  g2          <- g
  V(g2)$label <- ifelse(!is.na(V(g2)$name), sprintf("%s [(%d/%d)]", V(g2)$name, shared_mlg, V(g2)$size), NA)
  glay        <- create_layout(g2, "manual", node.positions = as.data.frame(rbind(glayout, glayout)))
  x_nudge     <- ifelse(abs(glay$x) == 1, -glay$x/10, glay$x/10)
  breaks      <- quantile(1 - E(g)$weight)
  breaks      <- setNames(breaks, format(breaks, digits = 2))
  outg <- ggraph(glay) +
    geom_edge_fan(aes(alpha = 1 - weight, width = width + 1)) +
    geom_node_circle(aes(r = drop(scale(size, center = FALSE))/10, fill = size))
  outg <- if (label) outg + geom_node_label(aes(label = label), repel = TRUE, parse = TRUE, label.size = 0.75, nudge_x = x_nudge, segment.size = 0) else outg
  outg + 
    viridis::scale_fill_viridis(option = "C") +
    scale_edge_alpha_continuous(range = c(1, 0.25), breaks = rev(breaks)) +
    scale_edge_width_continuous(range = c(0.25, 1.25), breaks = c(2:5)) +
    coord_fixed() +
    theme_void() +
    theme(text = element_text(size = 14)) +
    labs(list(
     # title = "Shared MLGs across regions",
      fill = "Number of\nMLHs",
      edge_alpha = "Probability of\nsecond encounter",
      edge_width = "Populations\nper MLH"#,
      #caption = "Outer circle: Number of MLGs in the region\nInner Circle: Number of private MLGs in the region"
    ))
}
